\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-01 syntax.tex

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using \ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will lead to problem because every field in linkage has this implicit universal quantification, and for this case we can substitute $a$ with arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top \to \bot}$ is a contradiction\YZ{You are talking about
overriding here, but you haven't told the reader what overriding means
in your metatheory.}\EDJreply{Ok. I use the projection now instead.}}. This term is important for us to abstract the
concrete inductive type so that the later field can depend on the
``abstract interface'' (i.e. $\cL(\{a:\cU~;~b:a \to T\})$) and achieve \textit{code reuse}. \\ On the other hand,
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rule for existential
(also existential type just don't allow overriding\YZ{Why is it desired that this type in the context does not allow overriding (since it already says 'a : U')?}).
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{}\YZ{Why does this Sig not have a superscript?}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodType{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

>>>>

The reason we need this additional type construct of $\cC\sigma$ here is
to support \textit{code reuse}, as the rule of linkages hinders its
ability to do abstraction. Concretely speaking, (using surface syntax)
we don't have \\ $\goodTerm{\Gamma, \cL(\{a~:~\bW \sigma; b~:~a \to
T\})}{h}{\cL(\{a~:~\cU; b~:~a \to T\})}$\footnote{If we had one,
consider the case $T$ is bottom type and $\sigma$ is empty record and
thus $a$ is initially bottom type. Now the direct projection using
\ruleref{Sig Proj} $\goodTerm{\Gamma, a : \cU}{h.b}{a \to \bot}$ will
lead to problem because every field in linkage has this implicit
universal quantification, and for this case we can substitute $a$ with
arbitrary type, say $\top$: $\goodTerm{\Gamma}{h.b[a \mapsto \top]}{\top
\to \bot}$ is a contradiction}.
However, this underivable term is important for us to abstract the
concrete inductive type so that the later field can depend on the
``abstract interface'' (i.e. something like $\cL(\{a:\cU~;~b:a \to T\})$) and achieve \textit{code reuse}. 
\YZ{It reads as if you want to have 'h : L\{a : U, b : a -> T\}'. But it is problematic because it leads to inconsistency, as you describe in a footnote.}\EDJreply{Good point. I rephrased it so the introduction of sigma type is smoother. Please check.}
\\ The good news, we don't have to stick with $\cL(\sigma)$ to express the abstract interface. We can also use sigma type, and actually 
we do have $\goodTerm{\Gamma, (\Sigma a : \bW\sigma, a \to T)
}{h}{(\Sigma a : \cU, a \to T)}$ because of the rules for sigma type.\footnote{The intro rule for sigma type decides that there is no such implicit universal quantification happening.}
\YZ{This sentence still speaks of overriding. Explain in terms of projection instead?}\EDJreply{Fixed. Please check.}
Thus to allow abstraction happens, we need $\cC\sigma$ to compile a
linkage to module as a part of the context and we also need
\ruleref{Lnkg Compile} to specify the compilation from linkage to
module.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\sigma}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\sigma~R}{n}\YZ{Why does this Sig not have a superscript?}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\sigma~R)}
\quad n < N
}
{\goodTerm{\Gamma}{"prjR"~n~o}{("RecSig1"~(\pi_1^n \sigma)~(\pi_2^n \sigma)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\sigma}{N}
\quad \goodType{\Gamma}{T}{\bW \sigma}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\sigma~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$
